Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper.tex
changed title
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@850 d8b0c59b-6544-0410-94d9-83a5658a058e

% first the title is needed
\title{An improved platform for Web service wrapping, discovery and consumption}

% a short form should be given in case it is too long for the running head
\titlerunning{Enhancing the discovery and consumption of Web services}

>>>>

% first the title is needed
\title{Web Service Wrapping, Discovery and Consumption --- More Power to the End-User}

% a short form should be given in case it is too long for the running head
\titlerunning{Web Service Wrapping, Discovery and Consumption --- More Power to the End-User}
